\documentclass[11pt]{article}
\usepackage{amssymb}
\usepackage{textcomp}
\newcommand{\numpy}{{\tt numpy}}    % tt font for numpy

\topmargin -1in
\textheight 9in
\oddsidemargin -.25in
\evensidemargin -.25in
\textwidth 7in

\begin{document}

\author{Pouya Aghahoseini 9513006}
\title{Exercise 1}
\maketitle

\medskip
	{\textbf{\huge Improve The Writing:}}
% ========== Begin answering questions here
\begin{enumerate}
\item
There are 3 special cases. \textrightarrow \hspace*{0.25cm}  There are three special cases.
\item
It does not tend to infinaty. \textrightarrow \hspace*{0.25cm} It does not tend to infinity.
\item
$\therefore c^{-1}$ is undefined. \textrightarrow \hspace*{0.25cm} therefore $c^{-1}$ is undefined.
\item
We square the equation. \textrightarrow \hspace*{0.25cm} We square both sides of the equation. 
\item
$x^{2} = y^{2}$ are two othogonal lines. \textrightarrow \hspace*{0.25cm} The equation $x^{2}=y^{2}$ represents two orthogonal lines. 
\item
This set of matrixs are all invertible. \textrightarrow \hspace*{0.25cm} This set consists of invertible matrices.
\item
Purely imaginary is when the real part is zero. \textrightarrow \hspace*{0.25cm} Purely imaginary means that the real part is zero. (If the real part is zero, then the number is purely imaginary.)
\item
From the fact that x = 0, I can't divide by x. \textrightarrow \hspace*{0.25cm} Since x is zero, I can’t divide by x. (I can't divide by $x$, because $x=0$.)
\item
The function f is not discontinuous. \textrightarrow \hspace*{0.25cm} The function f is continuous.
\item
The solution is not independent of s. \textrightarrow \hspace*{0.25cm} The solution depends on s.
\end{enumerate}
\textbf{\huge Exercise 1:}\\
\begin{enumerate}
	\item
	X is a finite set. \textrightarrow \hspace*{0.25cm} The set X is finite.
	\item
	It follows $x-1=y^{4}$. \textrightarrow \hspace*{0.25cm} hence(it follows that) $x-1=y^{4}$.
	\item
	The product of 2 negatives is positive. \textrightarrow \hspace*{0.25cm} Multiplying two negative numbers results in a positive number. (The product of two negative numbers is a positive number.) 
	\item
	We have less solutions than we had before. \textrightarrow \hspace*{0.25cm}	We have fewer solutions than we had before.
	\item
	Let us device a strategy for a proof. \textrightarrow \hspace*{0.25cm} here is a strategy for the proof. (Let us consider/use/find a strategy for the proof.)
	\item
	If the integral = 0 the function is undefined. \textrightarrow \hspace*{0.25cm} If the integral equals 0, then the function is undefined.
	\item
	Construct the set of vertex of triangles. \textrightarrow \hspace*{0.25cm}  Construct the set of all vertexes of triangles.
	\item
	A circle is when major and minor axis are the same. \textrightarrow \hspace*{0.25cm} A circle is a shape with equal major and minor axes.
	\item
	Plug-in that expression in the other equation. \textrightarrow \hspace*{0.25cm} Add that expression to both sides of the other equation.
	\item
	I found less solutions than I expected. \textrightarrow \hspace*{0.25cm} I found fewer solutions than I expected.
	\item
	When the discriminant is < 0, you get complex. \textrightarrow \hspace*{0.25cm} You get complex results if the discriminant is negative. (If the discriminant is negative, you get complex results.)
	\item
	We prove Euler theorom. \textrightarrow \hspace*{0.25cm} We prove Euler's theorem.
	\item
	The definate integral is where you don't have integration limits. \textrightarrow \hspace*{0.25cm} An integral is definite when it doesn't have integration limits.
	(If an integral doesn't have integration limits, it is definite.) 
	\item
	The asyntotes of this hiperbola are othogonal. \textrightarrow \hspace*{0.25cm} The asymptotes of this hyperbola are orthogonal.
	\item
	A quadratic function has 1 stationery point. \textrightarrow \hspace*{0.25cm} A quadratic function has only one stationary point.
	\item
	The solution is not independent of s. \textrightarrow \hspace*{0.25cm} The solution depends on s.
	\item
	a is negative $\therefore\sqrt{a}$ is complex. \textrightarrow \hspace*{0.25cm} a is negative, therefore $\sqrt{a}$(square root of a) is complex. 
	\item
	Thus x = a. (We assume that a is positive). \textrightarrow \hspace*{0.25cm} Thus x = a. (We assume that a is positive.)
	\item
	Each value is greater than their reciprical. \textrightarrow \hspace*{0.25cm} Each value is greater than its reciprocal.
	\item
	Remember to always check the sign. \textrightarrow \hspace*{0.25cm} Always remember to check the sign.
	\item
	Differentiate f n times. \textrightarrow \hspace*{0.25cm}  	Differentiate function f, repeating this process n times. 
\end{enumerate}

\end{document}
